---
title: "Getting in the Zone"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE
)
```

```{r load_pkgs, message=FALSE}
library(usps)
library(dplyr)
library(tidyr)
library(ggmap)
library(zipcode)
```

Data from the `zipcode` package relates zip codes to its latitude and longitude. 

```{r load_zips}
data("zips_zones")
data("zipcode")

zips <- 
  zipcode %>% 
  as_tibble() %>% 
  mutate(
    zip_trim = substr(zip, 1, 3)
  )

zips
```

Let's get a tibble of all possible USPS zips, both origin prefixes and destinations, including our 5 digit destinations.

```{r usps_zips, dependson="load_zips"}
usps_zips <-
  tibble(
    zip =
      unique(zips_zones$origin_zip) %>% 
      c(unique(zips_zones$dest_zip)) 
  ) %>% 
  distinct()
```


Now we can join the `zipcode` latitudes and longitudes on our `usps_zips` to get a corresponding lat and long for each origin and destination zip.

```{r zips_lat_long}
zips_lat_long <- 
  zips %>% 
  distinct(zip_trim, .keep_all = TRUE) %>% 
  left_join(usps_zips, by = "zip") %>% 
  select(zip_trim, latitude, longitude)
```


```{r zips_zones_lat_long}
zips_zones_lat_long <- 
  zips_zones %>% 
  left_join(zips_lat_long, by = c("origin_zip" = "zip_trim")) %>% 
  rename(
      lat_origin = latitude,
      long_origin = longitude) %>% 
  left_join(zips_lat_long, by = c("dest_zip" = "zip_trim")) %>% 
  rename(
      lat_dest = latitude,
      long_dest = longitude) %>% 
  drop_na(zone)

zips_zones_lat_long
```


Using a single origin zip, we can plot all of the destination zips' zones relative to that origin. 

```{r us_map, eval=TRUE}
us <- 
  get_googlemap("us", zoom = 4)
  # get_map("us", zoom = 4, maptype = "toner-lite")
```


```{r zone_map, eval=TRUE}
ggmap(us, extent = "device") +
  geom_polygon(data = zips_zones_lat_long %>% 
                 mutate(zone = factor(zone)) %>% 
                 filter(origin_zip == "112"), 
             aes(long_dest, lat_dest, fill = zone),
             alpha = 0.5) +
  labs(x = "", y = "", fill = "Zone") +
  ggtitle("Shipping Zones from Brooklyn",
          subtitle = "Origin zone prefix: 112") +
  scale_fill_brewer(type = "seq") +
  theme_classic(base_family = "Arial Narrow")
```


<br>
